\thesistitle

### 2019-06-16 sections/research.tex
Better math

$$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
$$\text{Diff = Amount that differ from other clone instances in the clone class}$$
$$\text{Total = Total number in the clone instance}$$
$$\text{l = Number of literals}$$
$$\text{v = Number of variables}$$
$$\text{m = Number of method calls}$$
$$\text{t = Number of tokens}$$

@@

$$T3R\ Gap\ Percentage=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
$$Statements = The\ amount\ of\ statements\ in\ this\ code\ fragment$$
$$C_{gap} = The\ gap between two clones$$
$$C_{above} = The\ clone\ instance\ above\ the\ gap$$
$$lower = The clone instance below the gap$$

>>>>

$$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
$$Diff = \text{Amount that differ from other clone instances in the clone class}$$
$$Total = \text{Total number in the clone instance}$$
$$l = \text{Number of literals}$$
$$v = \text{Number of variables}$$
$$m = \text{Number of method calls}$$
$$t = \text{Number of tokens}$$

@@

$$\text{T3R Gap Percentage}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
$$Statements = \text{The amount of statements in this code fragment}$$
$$C_{gap} = \text{The gap between two clones}$$
$$C_{above} = \text{The clone instance above the gap}$$
$$C_{below} = \text{The clone instance below the gap}$$
